---
title: "Final Project"
author: "Nguyen SM"
date: "2024-04-24"
output: word_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(readxl)
Nguyen_screentime<-read_excel("Nguyen_screentime.xlsx")
library(tidyverse)
```

# Null Testing
## Claim: Gym attendance is less likely with more hours of screen time than hours of rest time.
$P_s$: Proportion of gym attendance with higher screen time
$P_r$: Proportion of gym attendance with higher rest time
$H_0:P_s=P_r$ vs $H_a:P_s<P_r$
```{r}
table(Nguyen_screentime$Gym)
Nguyen_screentime_data<-Nguyen_screentime%>%
  filter(Gym%in%c("YES"))
Nguyen_screentime_data

t.test(Nguyen_screentime_data$Screentime,Nguyen_screentime_data$Rest,paired="TRUE")

Nguyen_screentime_graph<-Nguyen_screentime_data%>%
  mutate(`Higher Screentime`=if_else(Nguyen_screentime_data$Screentime>Nguyen_screentime_data$Rest,"Yes","No"))%>%
  ggplot(aes(x=`Higher Screentime`))+geom_bar()+labs(y="Attendance Count")
Nguyen_screentime_graph
```
p-value=0.06923>0.05
Accept the $H_0$.
At 5% significance level, we do not have sufficient evidence to conclude that gym attendance is likelier with a higher rest time.